---
title: "SI Project 2"
author: "Kun Qian"
date: "Thursday, February 12, 2015"
output: html_document
---
In the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package. 

#### 1.Load the ToothGrowth data and perform some basic exploratory data analyses 
```{r}
library(datasets)
data(ToothGrowth)
```

#### 2.Provide a basic summary of the data.
```{r}
head(ToothGrowth)
dim(ToothGrowth)
summary(ToothGrowth)
```
The data is set of 60 observations, length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1 and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

As can be seen below, there is a clear positive correlation between the tooth length and the dose levels of Vitamin C, for both delivery methods.
```{r}
library(datasets)
library(ggplot2)
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
    geom_bar(stat="identity",) +
    facet_grid(. ~ supp) +
    xlab("Dose in miligrams") +
    ylab("Tooth length") +
    guides(fill=guide_legend(title="Supplement type"))
```

#### Confidence Intervals
We first consider a test of average difference between group using VC and OJ. In order to do that, we use unequal variance t test
```{r}
t.test(len ~ supp, paired = F, var.equal = F, data = ToothGrowth)
```
As shown in the result, 0 is contained in the 95% confidence interval. Given p-value is 0.06 > 0.05, we cannot reject the null hypothesis that true difference in means is equal to 0

Now we consider dose variable. First we seperate data into different groups:
```{r}
dose12 <- subset(ToothGrowth, dose %in% c(0.5, 1))
dose23 <- subset(ToothGrowth, dose %in% c(1, 2))
dose13 <- subset(ToothGrowth, dose %in% c(0.5, 2))
```
Then we perform unequal variance t test for each of the group:
```{r}
t.test(len ~ dose, paired = FALSE, var.equal = FALSE, data = dose12)
t.test(len ~ dose, paired = FALSE, var.equal = FALSE, data = dose23)
t.test(len ~ dose, paired = FALSE, var.equal = FALSE, data = dose13)
```
These results show either 2 groups have significant different means leading to the conclusion that using different dose cause different lens on average. 

#### Regression approach
We could also use simple linear regression to test the relationship between variables:
```{r}
fit <- lm(len ~ dose + supp, data=ToothGrowth)
summary(fit)
confint(fit)






